% !TeX root = cover.tex

% I am writing to express interest in the Cryptography Researcher position at \company. With my strong background in cryptography coupled with my ability to perform high-quality research, I am confident my skills
I am writing to express interest in the \position position at \company, as advertised on your website. With my strong background in cryptography, capacity to perform high-quality research, and problem-solving skills, I am eager to contribute to your team and support 
\companys goals of 
% building the first cryptographic computer.
solving challenging problems through cryptography.
% building secure, decentralized digital asset management systems.

% minimizing the potential harm of MEV for Ethereum-based blockchains.
% and support 
% the mission of \company
% your mission to 
% I am eager to contribute to 
% % and advance
% \company' goal of of developing

Currently, I am nearing completion of my PhD in Computer Science from the University at Buffalo, where I specialize in secure multi-party computation (SMC) and its applications. Throughout my PhD, I have worked on a variety of projects ranging from classical protocol construction (design, prototyping, and implementation), to developing novel methodologies for quantifying information disclosure from arbitrary secure function evaluations. 
My research in this space has resulted in several publications in top security conferences and awards for my work. 

Beyond my central focus of SMC, I have interfaced with other branches of cryptography through my research, including differential privacy, input certification, and zero-knowledge proofs. Additionally, I previously conducted research on blockchain applications in healthcare, where our group proposed one of the first smart contract-based remote patient monitoring systems.

My prior experience with blockchain, coupled with my expertise in cryptography drew me to \companys mission of 
utilizing cutting-edge cryptographic techniques to solve problems with practical significance.
% solving 
% bridging the gap between  and customer-facing applications.
% providing secure and scalable solutions for digital assets,
% My prior experience drew me to \companys mission of integrating cryptography at a fundamental level into next-generation technologies.
% mitigating the negative consequences of MEV, 
% This presents the opportunity to a broad range of opportunities to develop cutting-edge cryptographic solutions. 
% Your work 
% Specifically,
% due to the broad range of opportunities to develop cutting-edge cryptographic solutions. Specifically, 
% the secret sharing component of the Lock-Keeper system 
% your work on verifiable secret sharing 
% your work on multi-party computation and multi-signature schemes 
This philosophy directly aligns with my background in designing and implementing performant SMC protocols for end-user deployment.
To this end, my work as the primary maintainer of our group's large-scale open-source SMC compiler facilitated my growth as both a developer and researcher.
In parallel with optimizing existing solutions and writing new protocol implementations, I also mentor and advise my team members working on the compiler.
This project honed my skills in software engineering, collaboration, and problem-solving, while demonstrating my ability to efficiently deliver high-quality work and lead others.
% gained valuable experience developing and maintaining software 
% through my work on our group's large-scale open-source SMC compiler.

% Furthermore, I am actively part of an ongoing project for building frameworks for secure computation with certified inputs. This carries direct applications in blockchain-based applications by enforcing correctness and accountability across computational participants.

% My responsibilities include  
% research on accountability in multi-party computation is directly related to an ongoing project 
% the research problem of guaranteeing cryptographic privacy for searchers is attractive since it  for deployment in untrusted environments.
% ,  and interest in building privacy enhancing technologies.

I appreciate and thank you for considering my application. 
I look forward to the opportunity to discuss how my cryptography expertise and skills align with those of \company.
% about the prospect of contributing my cryptography expertise to \company and furthering (the goal of XXX).
% I look forward to the opportunity to meet and discuss the position in more detail. 
Please feel free to contact me at \myphone or \myemail. 
% Thank you for your time.


% I want to be able to leverage my epxerience in secure multi-party computation to solve real-world problems in the crytpo space.
