
\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[colorlinks=true]{hyperref}
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.7}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

\usepackage{fancyhdr}
\usepackage{inconsolata}
\usepackage[english]{babel}
\usepackage{tabularx}
 
% \usepackage[sfdefault,lining,light]{FiraSans}
% \usepackage[sfdefault,lining]{FiraSans}
% \usepackage{noto}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheadingDesc}[6]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, #2 & #3 \\
        \textit{\small#4} {\small#5} & {\small #6} 
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubDesc}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        {\small#1} & {\small #2}
    \end{tabular*}\vspace{-20pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={}]}
        \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.20in]}
        \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Alessandro Baccarini} \\ \vspace{1pt}
    \small \href{tel:19148863901}{\faicon{phone} +1 914 886 3901}  
    $|$
    \href{mailto:abaccarini@proton.me}{{\faicon{inbox} abaccarini@proton.me}} 
    $|$
    \href{https://abaccarini.github.io/}{{\faicon{globe} \url{abaccarini.github.io}}} 
    $|$
    \href{https://www.linkedin.com/in/alessandro-baccarini/}{{\faicon{linkedin} LinkedIn}} 
    % $|$
    % \href{https://github.com/abaccarini}{{\faicon{github-alt} GitHub (\texttt{abaccarini})}}
\end{center}




%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheadingDesc
{University at Buffalo}{Buffalo, NY}{Aug. 2019 -- Aug. 2024}
{Ph.D., Computer Science,}{Advisor: Marina Blanton}{}
\resumeItemListStart
\resumeItem{Dissertation: \emph{New Directions in Secure Multi-Party Computation: Techniques and Information Disclosure Analysis}}
\resumeItemListEnd
% \resumeSubSubDesc
% {Advised by Marina Blanton}{}
% \resumeSubSubDesc
% {Dissertation: New Directions in Multi-Party Computation Techniques and Information Disclosure Evaluation for Data Analytics}{}
\resumeSubheadingDesc
{Fordham University}{Bronx, NY}{Aug. 2013 -- May 2019}
{M.S., Cybersecurity,}{Advisor: Thaier Hayajneh}{}
% {M.Sc., Cybersecurity}{}{2019}
\resumeSubSubheading
{B.S., Physics, Mathematics Minor}{}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheadingDesc
{Doctoral Researcher}{University at Buffalo}{Jan. 2020 -- Present}
{Secure Multi-Party Computation and Privacy-Preserving Machine Learning}{}{
    \href{https://github.com/anbaccar/RSS_ring_ppml}{{Repository}}
}
% % {PICCO Compiler}{University at Buffalo}
% % Throughout my Ph.D., I have worked in the following areas:
% \resumeSubSubheading
% % {PICCO Compiler}{Jan 2020 - Present}
% {Secure Multi-Party Computation}{}
\resumeItemListStart
\resumeItem{Designed and implemented a comprehensive framework of state-of-the-art multi-party protocols based on replicated secret sharing, resulting in an up to $33 \times $ performance gain over existing secret sharing techniques.}
% \resumeItem{Cutting-edge cryptographic techniques in secure multi-party computation.}
\resumeItem{Applied our framework to several privacy-preserving machine learning tasks, and discovered a new optimization technique for secure quantized neural network inference, leading to a $2\times$ improvement over prior works.}
% \resumeItem{Implemented protocol suite in C++, later on merging the framework into the PICCO compiler.}
\resumeItemListEnd
\resumeSubSubheading
{PICCO Compiler}{
    \href{https://github.com/applied-crypto-lab/picco}{{Repository}}
}
\resumeItemListStart
\resumeItem{Core maintainer of \emph{PICCO}, a source-to-source compiler used to translate general-purpose programs into their secure implementations for deployment in a distributed setting.}
\resumeItem{Integrated novel techniques o}
\resumeItem{Extensively optimized existing protocol implementations, while simultaneously performing a large-scale refactor in order to support future maintainability and extensibility.}
% \resumeItem{Integrated replicated secret sharing framework into the compiler.}
% \resumeItem{Mentored undergraduate student on network-level optimizations.}
\resumeItemListEnd
\resumeSubSubheading
{Disclosure Analysis from Secure Function Evaluation}{
\href{https://github.com/anbaccar/estimators}{{Repository}}
}
\resumeItemListStart
\resumeItem{Developed a novel approach for evaluating private information disclosure from secure function evaluation based on information-theoretic principles.}
\resumeItem{Performed both analytical and simulation-based analysis on a variety of descriptive statistical functions.}
\resumeItem{Awarded first place \$2000 cash prize from the Alan Selman Scholarship for theoretical computer science for this work.}
\resumeItemListEnd

\resumeSubheadingDesc
{Graduate Research Assistant}{Fordham University}{Aug. 2017 -- May 2019}
{Blockchain Applications in Healthcare}{}{}
\resumeItemListStart
\resumeItem{Led the design on one of the earliest frameworks that fused blockchain and healthcare together into an IoT remote patient monitoring system based on the Ethereum protocol.}
\resumeItem{Assisted in prototype smart contract development in Solidity to support real-time automated monitoring.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Publications-----------
\section{Selected Publications}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Conference Proceedings}}{}
\resumeItemListStart
\resumeItem{\textbf{A. Baccarini}, M. Blanton, S. Zou, ``Understanding Information Disclosure from Secure Computation Output: A Study of Average Salary Computation.'' \href{https://dl.acm.org/doi/abs/10.1145/3626232.3653280}{\emph{ACM CODASPY}, 2024.}}
\resumeItem{\textbf{A. Baccarini}, M. Blanton, C. Yuan, ``Multi-Party Replicated Secret Sharing over a Ring with Applications to Privacy-Preserving Machine Learning.'' \href{https://petsymposium.org/2023/}{\emph{Privacy Enhancing Technologies Symposium (PETS)} }and \href{https://petsymposium.org/popets/2023/popets-2023-0035.php}{\emph{Proceedings on Privacy Enhancing Technologies (PoPETs)}, Vol. 2023, No. 1, 2023. }}
% \resumeItem{\textbf{A. Baccarini}, T. Hayajneh, ``Evolution of Format Preserving Encryption on IoT Devices: FF1+.'' \href{https://scholarspace.manoa.hawaii.edu/handle/10125/59603}{\emph{HICSS}, 2019.}}
% \resumeItem{A. Alhayajneh, \textbf{A. Baccarini}, T. Hayajneh,  ``Quality of Service Analysis of VoIP Services.''  \emph{IEEE UEMCON}, 2018.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Refereed Journals}}{}
\resumeItemListStart
\resumeItem{\textbf{A. Baccarini}, M. Blanton, S. Zou,  ``Understanding Information Disclosure from Secure Computation Output: A Comprehensive Study of Average Salary Computation.''  \emph{ACM Transactions on Privacy and Security (TOPS)}, to appear.}
\resumeItem{A. Alhayajneh, \textbf{A. Baccarini}, G.M. Weiss, T. Hayajneh, A.  Farajidavar,   ``Biometric Authentication and Verification for Medical Cyber Physical Systems.'' \href{https://www.mdpi.com/2079-9292/7/12/436}{\emph{Electronics}, 7(12), 436. 2018.}}
\resumeItem{K.N. Griggs, O. Ossipova, C.P. Kohlios, \textbf{A. Baccarini}, E.A. Howson, T. Hayajneh, ``Healthcare Blockchain System Using Smart Contracts for Secure Automated Remote Patient Monitoring.'' \href{https://link.springer.com/article/10.1007/s10916-018-0982-x}{\emph{J Med Syst}, 42: 130. 2018.} }
\resumeItemListEnd
\resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
          \textbf{Cryptographic Techniques}{: secure multi-party computation, secret sharing, differential privacy, private set intersection} \\
          \textbf{Languages}{: C/C++, Python, Bash, Lua, \LaTeX} \\
          \textbf{Developer Tools}{: Git, SVN, Neovim, VS Code } \\
          \textbf{Libraries}{: GNU MP and MPFR, OpenSSL, NumPy, SciPy, Matplotlib, TensorFlow}
          }}
\end{itemize}


%-------------------------------------------
\end{document}

